%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Embedded Developer} % Job title
    {Quanta Computer Inc.} % Organization
    {Taoyuan} % Location
    {Jun. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Ported OpenBMC system into existing server based Aspped SoC.}
        \item {Boot up OpenBMC system into extension BMC Module based Nuvoton SoC.}
        \item {Implemented NVMe hot swapping power controll on BMC.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Back-end Web Developer} % Job title
    {Quanta Computer Inc.} % Organization
    {Taoyuan} % Location
    {Mar. 2018 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented controll server's PSU feature on server Management system. \\
            e.g: read server's PSU related informations or update cold redundant setting by IPMI command.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
  {DevOps and QA Developer} % Job title
  {Quanta Computer Inc.} % Organization
  {Taoyuan} % Location
  {Jul. 2017 - Mar. 2018} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed the web intergration test structure by Behave and Selenium.}
      \item {Developed automatic UI intergration test workflow by Jenkins.}
      \item {Generated and managed tested environment by Vagrant and Ansible.}
      \item {Connected the Robot framework with the automatic system.}
      \item {Experiment transfer Jenkins and Selenium to Kubernetes.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Full-Stack Web Developer} % Job title
    {Gemtek Technologies Co. Ltd} % Organization
    {Hsinchu} % Location
    {Mar. 2016 - Apr. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Refactor web UI from Flash/Javascript to Bootstrap/JQuery.}
        \item {Developed AP captive portal workflow including advertising play and multiple login. \\
              e.g: login option which supported facebook, Google, App auth; advertising play like Free Wi-Fi on Bus, \\
              customed advertising interface by CKEditor.}
        \item {Responsible for AP Logged user management and history on AP manager server.\\
              e.g: recording user location, user level and handling wirless AP romaing user status.}
        \item {Refactor web framework form Struts2 to SpringMVC.}
        \item {Experiment dynamic advertising and App notication setting.\\
              e.g: dynamic advertising binding different AP Groups and notification by Firebase.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
